---
title: "logBF from Siming's data (cancer somatic)"
author: "weiwang"
date: YYYY-MM-DD
output: 
  html_document:
    css: layout/floating-toc.css
    toc: true
---

**Last updated:** `r Sys.Date()`

**Code version:** `r system("git log -1 --format='%H'", intern = TRUE)`

```{r chunk-options, include=FALSE}
source("layout/chunk-options.R")
```

## we got 17 factor for flash with colum wise variance structure

we check the factor and loading, and we also take the sign into account

### factor 1

- leading tissue : All
- relevant tissues : "STAD" "UCEC" 
- positive : "SKCM"
- negative : "BLCA" "BRCA" "CESC" "ESCA" "HNSC" "KIRC" "LIHC" "STAD" "UCEC"

for the loadings (genes)

- leading gene: "ABCC8"    "ANK3"     "ARID2"    "CASR"     "CNTNAP2"  "CRB1"     "CTCF"     "DNAH7"    "DSCAM"    "GRIN2B"   "HCN1"     "KIAA1109" "MGAM" "MYH1"     "MYO7B"    "PAPPA"    "PAPPA2"   "PBRM1"    "PPP6C"    "SCN10A"   "SCN11A"   "SDK1"     "SLC14A2"  "SYNE1"    "VHL" 
- positive gene: "ARID2"    "KIAA1109" "MYO7B"    "PPP6C"    "SDK1"     "SYNE1"
- negative gene: "ABCC8"   "ANK3"    "CASR"    "CNTNAP2" "CRB1"    "CTCF"    "DNAH7"   "DSCAM"   "GRIN2B"  "HCN1"    "MGAM"    "MYH1"    "PAPPA"   "PAPPA2" "PBRM1"   "SCN10A"  "SCN11A"  "SLC14A2" "VHL" 


### factor 2

- leading tissue : "SKCM"
- relevant tissues : "STAD" "UCEC" 
- positive : "SKCM"
- negative : "BLCA" "BRCA" "CESC" "ESCA" "HNSC" "KIRC" "LIHC" "STAD" "UCEC"

for the loadings (genes)

- leading gene: "ABCC8"    "ANK3"     "ARID2"    "CASR"     "CNTNAP2"  "CRB1"     "CTCF"     "DNAH7"    "DSCAM"    "GRIN2B"   "HCN1"     "KIAA1109" "MGAM" "MYH1"     "MYO7B"    "PAPPA"    "PAPPA2"   "PBRM1"    "PPP6C"    "SCN10A"   "SCN11A"   "SDK1"     "SLC14A2"  "SYNE1"    "VHL" 
- positive gene: "ARID2"    "KIAA1109" "MYO7B"    "PPP6C"    "SDK1"     "SYNE1"
- negative gene: "ABCC8"   "ANK3"    "CASR"    "CNTNAP2" "CRB1"    "CTCF"    "DNAH7"   "DSCAM"   "GRIN2B"  "HCN1"    "MGAM"    "MYH1"    "PAPPA"   "PAPPA2" "PBRM1"   "SCN10A"  "SCN11A"  "SLC14A2" "VHL" 

### factor 3

- leading tissue : "BLCA" "BRCA" "ESCA" "GBM"  "HNSC" "LGG"  "LIHC" "LUAD" "LUSC" "PAAD" "SARC" "STAD" "UCEC" "UCS"
- negative : all

for the loadings (genes)

- leading gene: "TP53"



## Session information

```{r info, echo = FALSE}
sessionInfo()
```
