---
title: "test the mix variance structure"
author: "wei"
date: 2016-10-25
output: 
  html_document:
    css: layout/floating-toc.css
    toc: true
---

**Last updated:** `r Sys.Date()`

**Code version:** `r system("git log -1 --format='%H'", intern = TRUE)`

```{r chunk-options, include=FALSE}
source("layout/chunk-options.R")
```

## generate data

```{r}
sim_data = function(N, P, SF, SL, signal,
                    a = rchisq(N,3), b = rchisq(P,1),
                    mu = 1, K = 6, positive = FALSE){
  
  E = matrix(rep(0,N*P),nrow=N)
  sig2_true = matrix(rep(0,N*P),nrow=N)
  for(i in 1:N){
    for(j in 1:P){
      sig2_true[i,j] = mu + a[i] * b[j]
      E[i,j] = rnorm(1,0,sqrt(sig2_true[i,j]))
    }
  }
  
  Y = E
  L_true = array(0, dim = c(N,K))
  F_true = array(0, dim = c(P,K))
  
  for(k in 1:K){
    lstart = rnorm(N, 0, signal)
    fstart = rnorm(P, 0, signal)
    
    index = sample(seq(1:N),(N*SL))
    lstart[index] = 0
    index = sample(seq(1:P),(P*SF))
    fstart[index] = 0
    
    if(positive == TRUE){
      lstart = abs(lstart)
      fstart = abs(fstart)
    }
    
    L_true[,k] = lstart
    F_true[,k] = fstart
    
    Y = Y + lstart %*% t(fstart)
  }
  
  return(list(Y = Y, L_true = L_true, F_true = F_true, Error = E,sig2_true = sig2_true))
}
```

## try the rank one case

### we set the variance is a constant plus a columnwise structure variance.

```{r}
set.seed(100)
N = 60
P = 100
SF = 0.5
SL = 0.8
data = sim_data(N, P, SF, SL, a = rep(1,N), b = rchisq(P,1), mu = 1.5, signal = 1,K = 1)

plot(svd(data$Y)$d)
# data$sig2_true

# First test the flash rank one case.
g_flash = flashr::flash(data$Y,partype = "noisy_col",sigmae2_true = matrix(1.5,ncol = P, nrow = N))
plot((data$sig2_true[1,]), g_flash$sigmae2[1,])
abline(0,1)


set.seed(100)
N = 60
P = 100
SF = 0.5
SL = 0.8
data = sim_data(N, P, SF, SL,a = rep(1,N), b = rchisq(P,1), mu = 0.2, signal = 2,K = 1)

plot(svd(data$Y)$d)
# data$sig2_true

# First test the flash rank one case.
g_flash = flashr::flash(data$Y,partype = "noisy_col",sigmae2_true = matrix(0.2,ncol = P, nrow = N))
plot((data$sig2_true[1,]), g_flash$sigmae2[1,])
abline(0,1)

```

### known constant plus a unknown constant

```{r}
set.seed(100)
N = 60
P = 100
SF = 0.5
SL = 0.8
data = sim_data(N, P, SF, SL,a = rep(1,N), b = rep(2,P), mu = 0.2, signal = 2,K = 1)

plot(svd(data$Y)$d)
g_flash = flashr::flash(data$Y,partype = "noisy",sigmae2_true = matrix(0.2,ncol = P, nrow = N))
c((data$sig2_true[1,1]), g_flash$sigmae2[1,1])

```

## test for the rank K, for the backfitting algorithm we only use 10 iterations

### known constant plus unknown constant

```{r}
set.seed(100)
N = 60
P = 100
SF = 0.5
SL = 0.8
data = sim_data(N, P, SF, SL,a = rep(1,N), b = rep(2,P), mu = 1, signal = 2,K = 6)
plot(svd(data$Y)$d)
g_flash = flashr::greedy(data$Y,K = 9,
                         flash_para = list(partype = "noisy",sigmae2_true = matrix(1,ncol = P, nrow = N)))
b_flash = flashr::backfitting(data$Y,initial_list = g_flash, maxiter_bf = 10, 
                              flash_para = list(partype = "noisy",sigmae2_true = matrix(1,ncol = P, nrow = N)))

c(data$sig2_true[1,1],(b_flash$sigmae2[[6]])[1,1])
```


### known constant plus unknows columnwise structure

```{r}
set.seed(100)
N = 60
P = 100
SF = 0.5
SL = 0.8
data = sim_data(N, P, SF, SL,a = rep(1,N), b = rchisq(P,1), mu = 1, signal = 2,K = 6)
plot(svd(data$Y)$d)
g_flash = flashr::greedy(data$Y,K = 9,
                         flash_para = list(partype = "noisy_col",sigmae2_true = matrix(1,ncol = P, nrow = N)))
b_flash = flashr::backfitting(data$Y,initial_list = g_flash, maxiter_bf = 10, 
                              flash_para = list(partype = "noisy_col",sigmae2_true = matrix(1,ncol = P, nrow = N)))
plot((data$sig2_true[1,]), (b_flash$sigmae2[[6]])[1,])
abline(0,1)
```


## Session information

```{r info, echo = FALSE}
sessionInfo()
```
